### 2006-01-22 article/Article.tex
add images to the article
darcs-hash:20060122210145-2fc9d-4b5b4cc3fe3c5741808d7e2eb9d7566e31773845.gz

%
% Complete documentation on the extended LaTeX markup used for Insight
% documentation is available in ``Documenting Insight'', which is part
% of the standard documentation for Insight.  It may be found online
% at:
%
%     http://www.itk.org/

\documentclass{InsightArticle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  hyperref should be the last package to be loaded.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvips,
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}
% to be able to use options in graphics
\usepackage{graphicx}
% for pseudo code
\usepackage{listings}
% subfigures
\usepackage{subfigure}

%  This is a template for Papers to the Insight Journal. 
%  It is comparable to a technical report format.

% The title should be descriptive enough for people to be able to find
% the relevant document. 
\title{}

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.00}

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{}
\authoraddress{}

\begin{document}
\maketitle

\ifhtml
\chapter*{Front Matter\label{front}}
\fi

\begin{abstract}
\noindent
% The abstract should be a paragraph or two long, and describe the
% scope of the document.
\end{abstract}

\tableofcontents

% \url{http://www.itk.org}
% \code{Insight/Documentation/Style.pdf}
% \section{Principles of Solar Spot Detection}
% \cite{ITKSoftwareGuide}.
% \doxygen{ImageToImageFilter}

% \small \begin{verbatim}
% \end{verbatim} \normalsize

% The {itemize} environment uses a bullet for each \item.  If you want the 
% \item's numbered, use the {enumerate} environment instead.
% \begin{itemize}
%   \item  Insight Toolkit 2.4.
%   \item  CMake 2.2
% \end{itemize}

% \ref{cthead1}

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.5]{maximum0}
\caption{Maximum projection, axe=0.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.5]{maximum1}
\caption{Maximum projection, axe=1.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.75]{maximum}
\caption{Maximum projection, axe=2.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.75]{minimum}
\caption{Minimum projection}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.75]{mean}
\caption{Mean projection.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.75]{median}
\caption{Median projection}
\end{figure}

% \begin{figure}[htbp]
% \centering
% \includegraphics[scale=0.75]{sum}
% \caption{Sum projection}
% \end{figure}

\appendix

\bibliographystyle{plain}
\bibliography{InsightJournal}
\nocite{ITKSoftwareGuide}

\end{document}

### 2006-01-22 article/Article.tex
write the article
darcs-hash:20060122220909-2fc9d-5101590b3bd35727465dc5294e67e16f6420a655.gz

@@
 % the relevant document. 
-\title{}
+\title{Image projections along an axe}
 
@@
 % The author and/or editor can define 'significant' however they like.
-\release{0.00}
+% \release{0.00}
 
@@
 % snail-mail address if you like.
-\author{}
-\authoraddress{}
+\author{Ga\"etan Lehmann}
+\authoraddress{Unit\'e de Biologie du D\'eveloppement et de la Reproduction, Institut National de la Recherche Agronomique, 78350 Jouy-en-Josas, France}
 
@@
 \noindent
-% The abstract should be a paragraph or two long, and describe the
-% scope of the document.
+Image projection is a very common task in image analysis to reduce the dimension
+of an image. A base filter is provided with some specialized filters which
+implement different projection methods.
 \end{abstract}
 
-\tableofcontents
+% \tableofcontents
 
-% \url{http://www.itk.org}
-% \code{Insight/Documentation/Style.pdf}
-% \section{Principles of Solar Spot Detection}
-% \cite{ITKSoftwareGuide}.
-% \doxygen{ImageToImageFilter}
+\section{Introduction}
+ITK already provide a class to project an image along an axe:
+\doxygen{AccumulateImageFilter}. However, this class is limited to sum
+projection and mean projection.
 
-% \small \begin{verbatim}
-% \end{verbatim} \normalsize
+\section{Implementation}
 
-% The {itemize} environment uses a bullet for each \item.  If you want the 
-% \item's numbered, use the {enumerate} environment instead.
-% \begin{itemize}
-%   \item  Insight Toolkit 2.4.
-%   \item  CMake 2.2
-% \end{itemize}
+The base class, ProjectionImageFilter, is mainly a copy of
+AccumulateImageFilter, with some enhancement:
+\begin{itemize}
+  \item projection is delegated to a functor
+  \item report its progress
+\end{itemize}
+Different projection types are provided, with specialized classes:
+\begin{itemize}
+  \item maximum projection (MaximumProjectionImageFilter)
+  \item minimum projection (MinimumProjectionImageFilter)
+  \item mean projection (MeanProjectionImageFilter)
+  \item median projection (MedianProjectionImageFilter)
+  \item sum projection (SumProjectionImageFilter)
+\end{itemize}
+Other projections types can easily be created just by providing a new functor.
 
-% \ref{cthead1}
+AccumulateImageFilter is not modifiable to implement functor support without
+breaking the API.
+
+\section{Performance}
+
+A timing test comparing performance on a $371 \times 371 \times 34$
+image showed that the results are similar with AccumulateImageFilter
+and the equivalent ProjectionImageFilter, and that the new projection
+types have similar performance. The results achieved on an Athlon 64 
+Processor 2800+ (1802 MHz) with 512Kb cache, 512 Mb of RAM and gcc
+4.0.2 are shown in Table~\ref{perf}.
+
+\begin{table}[htbp]
+\centering
+\begin{tabular}{cc}
+\hline
+Filter & execution time \\
+\hline
+\hline
+MaximumProjectionImageFilter & 0.652 s \\
+MinimumProjectionImageFilter  & 0.614 s\\
+SumProjectionImageFilter  & 0.614 s\\
+MeanProjectionImageFilter  & 0.619 s\\
+MedianProjectionImageFilter  & 0.831 s\\
+AccumulateImageFilter, sum  & 0.615 s\\
+AccumulateImageFilter, mean  & 0.617 s\\
+\hline
+\end{tabular}
+\caption{Execution time.\label{perf}}
+\end{table}
+
+\section{Examples}
+Figure~\ref{maximum0}, Figure~\ref{maximum1}, Figure~\ref{maximum}, Figure~\ref{minimum}, Figure~\ref{mean} and Figure~\ref{median} show the result of different projection on different axes.
+The result of SumProjectionImageFilter in similar to the result of MeanProjectionImageFilter, but with a higher range of values, and so is not shown here.
 
@@
 \includegraphics[scale=0.5]{maximum0}
-\caption{Maximum projection, axe=0.}
+\caption{MaximumProjectionImageFilter, projection along axe x.\label{maximum0}}
 \end{figure}
@@
 \includegraphics[scale=0.5]{maximum1}
-\caption{Maximum projection, axe=1.}
+\caption{MaximumProjectionImageFilter, projection along axe y.\label{maximum1}}
 \end{figure}
@@
 \includegraphics[scale=0.75]{maximum}
-\caption{Maximum projection, axe=2.}
+\caption{MaximumProjectionImageFilter, projection along axe z.\label{maximum}}
 \end{figure}
@@
 \includegraphics[scale=0.75]{minimum}
-\caption{Minimum projection}
+\caption{MinimumProjectionImageFilter, projection along axe z.\label{minimum}}
 \end{figure}
@@
 \includegraphics[scale=0.75]{mean}
-\caption{Mean projection.}
+\caption{MeanProjectionImageFilter, projection along axe z.\label{mean}}
 \end{figure}
@@
 \includegraphics[scale=0.75]{median}
-\caption{Median projection}
+\caption{MedianProjectionImageFilter, projection along axe z\label{median}}
 \end{figure}
 
-% \begin{figure}[htbp]
-% \centering
-% \includegraphics[scale=0.75]{sum}
-% \caption{Sum projection}
-% \end{figure}
+\section{Sample code}
+
+\small \begin{verbatim}
+#include "itkImageFileReader.h"
+#include "itkImageFileWriter.h"
+#include "itkCommand.h"
+#include "itkSimpleFilterWatcher.h"
+
+#include "itkMaximumProjectionImageFilter.h"
+#include "itkExtractImageFilter.h"
+
+int main(int, char * argv[])
+{
+  int axe = atoi(argv[1]);
+
+  typedef unsigned char PType;
+  typedef itk::Image< PType, 3 > IType;
+  typedef itk::Image< PType, 2 > IType2;
+
+  typedef itk::ImageFileReader< IType > ReaderType;
+  ReaderType::Pointer reader = ReaderType::New();
+  reader->SetFileName( argv[2] );
+
+  typedef itk::MaximumProjectionImageFilter< IType, IType > FilterType;
+  FilterType::Pointer filter = FilterType::New();
+  filter->SetInput( reader->GetOutput() );
+  filter->SetAxe( axe );
+
+  itk::SimpleFilterWatcher watcher(filter, "filter");
+
+  filter->Update();
+
+  IType::SizeType inputSize = filter->GetOutput()->GetLargestPossibleRegion().GetSize();
+
+  typedef itk::ExtractImageFilter< IType, IType2 > ExtractType;
+  ExtractType::Pointer extract = ExtractType::New();
+  extract->SetInput( filter->GetOutput() );
+
+  IType::SizeType size;
+  for(int i=0; i<=3; i++) {
+    if(i == axe) {
+      size[i] = 0;
+    } else {
+      size[i] = inputSize[i];
+     }
+  }
+  IType::IndexType idx;
+  idx.Fill(0);
+
+  IType::RegionType region;
+  region.SetSize( size );
+  region.SetIndex( idx );
+  extract->SetExtractionRegion( region );
+
+  typedef itk::ImageFileWriter< IType2 > WriterType;
+  WriterType::Pointer writer = WriterType::New();
+  writer->SetInput( extract->GetOutput() );
+  writer->SetFileName( argv[3] );
+  writer->Update();
+
+  return 0;
+}
+\end{verbatim} \normalsize
+
+\section{Conclusion}
+The new classes give more feature and more flexibility with equivalent
+performance than the current available filter, but loss the compatibility with
+the previous filter. I propose to mark AccumulateImageFilter as deprecated in
+the next release of ITK to incite user to the new class.
+
+\section{Acknowledgments}
+We thank Dr Pierre Adenot and MIMA2 confocal facilities
+(\url{http://mima2.jouy.inra.fr})
+for providing image samples.
 

### 2006-01-22 itkMaximumProjectionImageFilter.h
enhance docstrings
darcs-hash:20060122222335-2fc9d-e6c3b13540ce51d51ccb5a0dd0ccfa518ef9e49f.gz

@@ -6,7 +6,9 @@
 
 namespace itk {
 /** \class MaximumProjectionImageFilter
- * \brief TODO
+ * \brief Maximum projection
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
  * \sa ProjectionImageFilter
  */

### 2006-01-22 itkMeanProjectionImageFilter.h

@@ -6,7 +6,9 @@
 
 namespace itk {
 /** \class MeanProjectionImageFilter
- * \brief TODO
+ * \brief Mean projection
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
  * \sa ProjectionImageFilter
  */

### 2006-01-22 itkMedianProjectionImageFilter.h

@@ -8,7 +8,9 @@
 
 namespace itk {
 /** \class MedianProjectionImageFilter
- * \brief TODO
+ * \brief Median projection
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
  * \sa ProjectionImageFilter
  */

### 2006-01-22 itkMinimumProjectionImageFilter.h

@@ -6,7 +6,9 @@
 
 namespace itk {
 /** \class MinimumProjectionImageFilter
- * \brief TODO
+ * \brief Minimum projection
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
  * \sa ProjectionImageFilter
  */

### 2006-01-22 itkProjectionImageFilter.h

@@ -36,15 +36,11 @@ namespace itk
  *
  *   The dimensions of the InputImage and the OutputImage must be the same.
  *
- *
- *
  * This class is parameterized over the type of the input image and
  * the type of the output image.
  *
- *
  * \author Emiliano Beronich
- *
- * This filter was contributed by Emiliano Beronich
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
  * \ingroup   IntensityImageFilters     Singlethreaded
  */

### 2006-01-22 itkSumProjectionImageFilter.h

@@ -6,7 +6,9 @@
 
 namespace itk {
 /** \class SumProjectionImageFilter
- * \brief TODO
+ * \brief Sum projection
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
  * \sa ProjectionImageFilter
  */

### 2006-01-30 itkMaximumProjectionImageFilter.h
give the projection size to the constructor
darcs-hash:20060130195551-2fc9d-34e22a6d8a927bb51fd5e84c84b93b98bcb83672.gz

@@ -19,7 +19,7 @@ template <class TInputPixel>
 class MaximumAccumulator
 {
 public:
-  MaximumAccumulator()
+  MaximumAccumulator( unsigned long size )
     {
     m_Maximum = NumericTraits< TInputPixel >::NonpositiveMin();
     }

### 2006-01-30 itkMeanProjectionImageFilter.h

@@ -19,26 +19,25 @@ template <class TInputPixel, class TOuputPixel>
 class MeanAccumulator
 {
 public:
-  MeanAccumulator()
+  MeanAccumulator( unsigned long size )
     {
     m_Sum = NumericTraits< TInputPixel >::Zero;
-    m_Count = 0;
+    m_Size = size;
     }
   ~MeanAccumulator(){}
 
   inline TInputPixel operator()( const TInputPixel &input )
     {
     m_Sum = m_Sum + input;
-    m_Count++;
     }
 
   inline TOuputPixel GetValue()
     {
-    return static_cast<TOuputPixel>( m_Sum / m_Count );
+    return static_cast<TOuputPixel>( m_Sum / m_Size );
     }
 
   typename NumericTraits< TOuputPixel >::AccumulateType m_Sum;
-  unsigned long m_Count;
+  unsigned long m_Size;
 };
 } // end namespace Function
 

### 2006-01-30 itkMedianProjectionImageFilter.h

@@ -21,7 +21,10 @@ template <class TInputPixel>
 class MedianAccumulator
 {
 public:
-  MedianAccumulator() {}
+  MedianAccumulator( unsigned long size )
+    {
+    m_Values.reserve( size );
+    }
   ~MedianAccumulator(){}
 
   inline TInputPixel operator()( const TInputPixel &input )

### 2006-01-30 itkMinimumProjectionImageFilter.h

@@ -19,7 +19,7 @@ template <class TInputPixel>
 class MinimumAccumulator
 {
 public:
-  MinimumAccumulator()
+  MinimumAccumulator( unsigned long size )
     {
     m_Minimum = NumericTraits< TInputPixel >::max();
     }

### 2006-01-30 itkSumProjectionImageFilter.h

@@ -19,7 +19,7 @@ template <class TInputPixel, class TOuputPixel>
 class SumAccumulator
 {
 public:
-  SumAccumulator()
+  SumAccumulator( unsigned long size )
     {
     m_Sum = NumericTraits< TInputPixel >::Zero;
     }

### 2006-01-30 itkMeanProjectionImageFilter.h
let the user choose the accumulate type
darcs-hash:20060130201957-2fc9d-308fa26e0f0f1d96eb1ba4f22915eb31806e8af8.gz

@@ -15,13 +15,13 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TOuputPixel>
+template <class TInputPixel, class TAccumulate>
 class MeanAccumulator
 {
 public:
   MeanAccumulator( unsigned long size )
     {
-    m_Sum = NumericTraits< TInputPixel >::Zero;
+    m_Sum = NumericTraits< TAccumulate >::Zero;
     m_Size = size;
     }
   ~MeanAccumulator(){}
@@ -31,27 +31,27 @@ public:
     m_Sum = m_Sum + input;
     }
 
-  inline TOuputPixel GetValue()
+  inline TAccumulate GetValue()
     {
-    return static_cast<TOuputPixel>( m_Sum / m_Size );
+    return m_Sum / m_Size;
     }
 
-  typename NumericTraits< TOuputPixel >::AccumulateType m_Sum;
+  TAccumulate m_Sum;
   unsigned long m_Size;
 };
 } // end namespace Function
 
 
-template <class TInputImage, class TOutputImage>
+template <class TInputImage, class TOutputImage, class TAccumulate=typename NumericTraits< typename TOutputImage::PixelType >::AccumulateType >
 class ITK_EXPORT MeanProjectionImageFilter :
     public
     ProjectionImageFilter<TInputImage, TOutputImage,
-      Function::MeanAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType > >
+      Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate > >
 {
 public:
   typedef MeanProjectionImageFilter Self;
   typedef ProjectionImageFilter<TInputImage, TOutputImage, 
-    Function::MeanAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType > > Superclass;
+    Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-01-30 itkSumProjectionImageFilter.h
use output pixel type traits
darcs-hash:20060130210055-2fc9d-e60d91946d06657ac697ddfa5700ef81d872c045.gz

@@ -21,7 +21,7 @@ class SumAccumulator
 public:
   SumAccumulator( unsigned long size )
     {
-    m_Sum = NumericTraits< TInputPixel >::Zero;
+    m_Sum = NumericTraits< TOuputPixel >::Zero;
     }
   ~SumAccumulator(){}
 

### 2006-01-30 article/Article.tex
add an example of implementation
darcs-hash:20060130210118-2fc9d-ba76003c9207a5292831ba53f2e0ffe3464ee5ba.gz

@@
 
+\section{Implemeting a new projection method}
+As an example, here is a filter which implement a square sum projection along a
+axe. This example may be useful in case of signed input type.
+
+Everything can be done in a single file, itkSquareSumProjectionImageFilter.h.
+\small \begin{verbatim}
+#ifndef __itkSquareSumProjectionImageFilter_h
+#define __itkSquareSumProjectionImageFilter_h
+\end{verbatim} \normalsize
+The itkProjectionImageFilter.h header must be included.
+\small \begin{verbatim}
+#include "itkProjectionImageFilter.h"
+#include "itkNumericTraits.h"
+
+namespace itk {
+
+namespace Function {
+\end{verbatim} \normalsize
+Now, create the class which do the real work: receive all the pixel values and
+give the result at the end. The class is created in the itk::Function names pace
+to avoid putting to much things in itk name space, and is templated over the
+type of the input and the output pixel.
+On object of this class is created for each pixel in the output image.
+\small \begin{verbatim}
+template <class TInputPixel, class TOuputPixel>
+class SquareSumAccumulator
+{
+public:
+\end{verbatim} \normalsize
+The constructor must take one parameter: the number of pixels to accumulate
+during the projection. In that case, this parameter is not useful, so it is not
+saved in an attribute of the class. The sum is initialized to zero.
+
+The destructor is empty - there is nothing to do.
+\small \begin{verbatim}
+  SquareSumAccumulator( unsigned long nb )
+    {
+    m_SquareSum = NumericTraits< TOuputPixel >::Zero;
+    }
+  ~SquareSumAccumulator(){}
+\end{verbatim} \normalsize
+The operator() is called for each pixel. In this method, the square sum is
+contructed, pixel after pixel. The method is declared inline for best
+performance.
+\small \begin{verbatim}
+  inline TInputPixel operator()( const TInputPixel &input )
+    {
+    m_SquareSum = m_SquareSum + ( input * input );
+    }
+\end{verbatim} \normalsize
+GetValue() is called to set the value of the result image. In that example, the
+sum is just return, but more complex computation can be done here (see the
+MedianProjectionImageFilter for an example). ProjectionImageFilter cast the
+output of this method to the output image's pixel type.
+\small \begin{verbatim}
+  inline TOuputPixel GetValue()
+    {
+    return m_SquareSum;
+    }
+\end{verbatim} \normalsize
+The internal attribute which accumulate the square sum.
+\small \begin{verbatim}
+  TOuputPixel m_SquareSum;
+};
+} // end namespace Function
+\end{verbatim} \normalsize
+The class is declared. It inherits from ProjectionImageFilter, and declares the
+usual types and methods.
+\small \begin{verbatim}
+template <class TInputImage, class TOutputImage>
+class ITK_EXPORT SquareSumProjectionImageFilter :
+    public
+    ProjectionImageFilter<TInputImage, TOutputImage,
+      Function::SquareSumAccumulator< typename TInputImage::PixelType,
+        typename TOutputImage::PixelType > >
+{
+public:
+  typedef SquareSumProjectionImageFilter Self;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, 
+    Function::SquareSumAccumulator< typename TInputImage::PixelType,
+      typename TOutputImage::PixelType > > Superclass;
+
+  typedef SmartPointer<Self>   Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Runtime information support. */
+  itkTypeMacro(SquareSumProjectionImageFilter, ProjectionImageFilter);
+
+  /** Method for creation through the object factory. */
+  itkNewMacro(Self);
+
+protected:
+  SquareSumProjectionImageFilter() {}
+  virtual ~SquareSumProjectionImageFilter() {}
+
+private:
+  SquareSumProjectionImageFilter(const Self&); //purposely not implemented
+  void operator=(const Self&); //purposely not implemented
+
+}; // end SquareSumProjectionImageFilter
+
+} //end namespace itk
+#endif
+\end{verbatim} \normalsize
+That's all.
+
 \section{Performance}
@@
 \section{Examples}
-Figure~\ref{maximum0}, Figure~\ref{maximum1}, Figure~\ref{maximum}, Figure~\ref{minimum}, Figure~\ref{mean} and Figure~\ref{median} show the result of different projection on different axes.
-The result of SumProjectionImageFilter in similar to the result of MeanProjectionImageFilter, but with a higher range of values, and so is not shown here.
+Figure~\ref{maximum0}, Figure~\ref{maximum1}, Figure~\ref{maximum},
+Figure~\ref{minimum}, Figure~\ref{mean} and Figure~\ref{median} show the result
+of different projection on different axes. The result of
+SumProjectionImageFilter in similar to the result of MeanProjectionImageFilter,
+but with a higher range of values, and so is not shown here.
 
@@
 the previous filter. I propose to mark AccumulateImageFilter as deprecated in
-the next release of ITK to incite user to the new class.
+the next release of ITK to incite ITK user to use the new class.
 

### 2006-02-11 itkMeanProjectionImageFilter.h
mean must be able to return a real type
darcs-hash:20060211120224-2fc9d-ae3a6010d5c7a0f1012aed1922cb7018e1d0e1f3.gz

@@ -19,6 +19,8 @@ template <class TInputPixel, class TAccumulate>
 class MeanAccumulator
 {
 public:
+  typedef typename NumericTraits<TInputPixel>::RealType RealType;
+
   MeanAccumulator( unsigned long size )
     {
     m_Sum = NumericTraits< TAccumulate >::Zero;
@@ -31,9 +33,9 @@ public:
     m_Sum = m_Sum + input;
     }
 
-  inline TAccumulate GetValue()
+  inline RealType GetValue()
     {
-    return m_Sum / m_Size;
+    return ((RealType) m_Sum) / m_Size;
     }
 
   TAccumulate m_Sum;

### 2006-02-11 itkSigmaProjectionImageFilter.h
add sigma projection
darcs-hash:20060211120717-2fc9d-d551ef7f2866c3802acb6209b295cb2667e56cc4.gz

@@ -1,0 +1,91 @@
+#ifndef __itkSigmaProjectionImageFilter_h
+#define __itkSigmaProjectionImageFilter_h
+
+#include "itkProjectionImageFilter.h"
+#include "itkNumericTraits.h"
+
+namespace itk {
+/** \class SigmaProjectionImageFilter
+ * \brief Mean projection
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \sa ProjectionImageFilter
+ */
+
+
+namespace Function {
+template <class TInputPixel, class TAccumulate>
+class SigmaAccumulator
+{
+public:
+  typedef typename NumericTraits<TInputPixel>::RealType RealType;
+
+  SigmaAccumulator( unsigned long size )
+    {
+    m_Sum = NumericTraits< TAccumulate >::Zero;
+    m_Size = size;
+    m_Values.reserve( size );
+    }
+  ~SigmaAccumulator(){}
+
+  inline TInputPixel operator()( const TInputPixel &input )
+    {
+    m_Sum = m_Sum + input;
+    m_Values.push_back( input );
+    }
+
+  inline RealType GetValue()
+    {
+    typename NumericTraits<TInputPixel>::RealType mean = ((RealType) m_Sum) / m_Size;
+    typename std::vector<TInputPixel>::iterator it;
+    RealType squaredSum = NumericTraits<RealType>::Zero;
+    for( it=m_Values.begin(); it!=m_Values.end(); it++ )
+      {
+      squaredSum += vnl_math_sqr(*it - mean);
+      }
+    return vcl_sqrt( squaredSum / ( m_Size - 1) );
+    }
+
+  TAccumulate m_Sum;
+  unsigned long m_Size;
+  std::vector<TInputPixel> m_Values;
+};
+} // end namespace Function
+
+
+template <class TInputImage, class TOutputImage, class TAccumulate=typename NumericTraits< typename TOutputImage::PixelType >::AccumulateType >
+class ITK_EXPORT SigmaProjectionImageFilter :
+    public
+    ProjectionImageFilter<TInputImage, TOutputImage,
+      Function::SigmaAccumulator< typename TInputImage::PixelType, TAccumulate > >
+{
+public:
+  typedef SigmaProjectionImageFilter Self;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, 
[…]

### 2006-02-11 itkMaximumProjectionImageFilter.h
pass index to the functor
darcs-hash:20060211162538-2fc9d-13c9c7977a487f64f4d0d97244a0166ceaeadd69.gz

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel>
+template <class TInputPixel, class TIndexType>
 class MaximumAccumulator
 {
 public:
@@ -25,7 +25,7 @@ public:
     }
   ~MaximumAccumulator(){}
 
-  inline TInputPixel operator()( const TInputPixel &input )
+  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {
     m_Maximum = vnl_math_max( m_Maximum, input );
     }
@@ -43,11 +43,11 @@ public:
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT MaximumProjectionImageFilter :
     public
-    ProjectionImageFilter<TInputImage, TOutputImage, Function::MaximumAccumulator< typename TInputImage::PixelType > >
+    ProjectionImageFilter<TInputImage, TOutputImage, Function::MaximumAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > >
 {
 public:
   typedef MaximumProjectionImageFilter Self;
-  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MaximumAccumulator< typename TInputImage::PixelType > > Superclass;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MaximumAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-11 itkMeanProjectionImageFilter.h

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TAccumulate>
+template <class TInputPixel, class TAccumulate, class TIndexType>
 class MeanAccumulator
 {
 public:
@@ -28,7 +28,7 @@ public:
     }
   ~MeanAccumulator(){}
 
-  inline TInputPixel operator()( const TInputPixel &input )
+  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {
     m_Sum = m_Sum + input;
     }
@@ -48,12 +48,12 @@ template <class TInputImage, class TOutputImage, class TAccumulate=typename Nume
 class ITK_EXPORT MeanProjectionImageFilter :
     public
     ProjectionImageFilter<TInputImage, TOutputImage,
-      Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate > >
+      Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate, typename TInputImage::IndexType > >
 {
 public:
   typedef MeanProjectionImageFilter Self;
   typedef ProjectionImageFilter<TInputImage, TOutputImage, 
-    Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate > > Superclass;
+    Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate, typename TInputImage::IndexType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-11 itkMedianProjectionImageFilter.h

@@ -17,7 +17,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel>
+template <class TInputPixel, class TIndexType>
 class MedianAccumulator
 {
 public:
@@ -27,7 +27,7 @@ public:
     }
   ~MedianAccumulator(){}
 
-  inline TInputPixel operator()( const TInputPixel &input )
+  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {
     m_Values.push_back( input );
     }
@@ -47,11 +47,11 @@ public:
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT MedianProjectionImageFilter :
     public
-    ProjectionImageFilter<TInputImage, TOutputImage, Function::MedianAccumulator< typename TInputImage::PixelType > >
+    ProjectionImageFilter<TInputImage, TOutputImage, Function::MedianAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > >
 {
 public:
   typedef MedianProjectionImageFilter Self;
-  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MedianAccumulator< typename TInputImage::PixelType > > Superclass;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MedianAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-11 itkMinimumProjectionImageFilter.h

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel>
+template <class TInputPixel, class TIndexType>
 class MinimumAccumulator
 {
 public:
@@ -25,7 +25,7 @@ public:
     }
   ~MinimumAccumulator(){}
 
-  inline TInputPixel operator()( const TInputPixel &input )
+  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {
     m_Minimum = vnl_math_min( m_Minimum, input );
     }
@@ -43,11 +43,11 @@ public:
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT MinimumProjectionImageFilter :
     public
-    ProjectionImageFilter<TInputImage, TOutputImage, Function::MinimumAccumulator< typename TInputImage::PixelType > >
+    ProjectionImageFilter<TInputImage, TOutputImage, Function::MinimumAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > >
 {
 public:
   typedef MinimumProjectionImageFilter Self;
-  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MinimumAccumulator< typename TInputImage::PixelType > > Superclass;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MinimumAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-11 itkSigmaProjectionImageFilter.h

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TAccumulate>
+template <class TInputPixel, class TAccumulate, class TIndexType>
 class SigmaAccumulator
 {
 public:
@@ -29,7 +29,7 @@ public:
     }
   ~SigmaAccumulator(){}
 
-  inline TInputPixel operator()( const TInputPixel &input )
+  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {
     m_Sum = m_Sum + input;
     m_Values.push_back( input );
@@ -58,12 +58,12 @@ template <class TInputImage, class TOutputImage, class TAccumulate=typename Nume
 class ITK_EXPORT SigmaProjectionImageFilter :
     public
     ProjectionImageFilter<TInputImage, TOutputImage,
-      Function::SigmaAccumulator< typename TInputImage::PixelType, TAccumulate > >
+      Function::SigmaAccumulator< typename TInputImage::PixelType, TAccumulate, typename TInputImage::IndexType > >
 {
 public:
   typedef SigmaProjectionImageFilter Self;
   typedef ProjectionImageFilter<TInputImage, TOutputImage, 
-    Function::SigmaAccumulator< typename TInputImage::PixelType, TAccumulate > > Superclass;
+    Function::SigmaAccumulator< typename TInputImage::PixelType, TAccumulate, typename TInputImage::IndexType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-11 itkSumProjectionImageFilter.h

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TOuputPixel>
+template <class TInputPixel, class TOuputPixel, class TIndexType>
 class SumAccumulator
 {
 public:
@@ -25,7 +25,7 @@ public:
     }
   ~SumAccumulator(){}
 
-  inline TInputPixel operator()( const TInputPixel &input )
+  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {
     m_Sum = m_Sum + input;
     }
@@ -44,12 +44,12 @@ template <class TInputImage, class TOutputImage>
 class ITK_EXPORT SumProjectionImageFilter :
     public
     ProjectionImageFilter<TInputImage, TOutputImage,
-      Function::SumAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType > >
+      Function::SumAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType, typename TInputImage::IndexType > >
 {
 public:
   typedef SumProjectionImageFilter Self;
   typedef ProjectionImageFilter<TInputImage, TOutputImage, 
-    Function::SumAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType > > Superclass;
+    Function::SumAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType, typename TInputImage::IndexType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-11 itkProjectionImageFilter.h
add a virtual NewAccumulator() method to create the accumulators
darcs-hash:20060211164158-2fc9d-e9165debded719991cf62cab15e8b65610689be7.gz

@@ -106,6 +106,8 @@ protected:
    *     ImageToImageFilter::GenerateData()  */
   void GenerateData(void);
 
+  virtual TAccumulator NewAccumulator( unsigned long );
+
 private:
   ProjectionImageFilter(const Self&); //purposely not implemented
   void operator=(const Self&); //purposely not implemented

### 2006-02-11 itkProjectionImageFilter.h
declare accumulator type
darcs-hash:20060211173548-2fc9d-ccfda405022f914366a101f0af9447d3a5ab4295.gz

@@ -70,6 +70,7 @@ public:
   typedef typename     OutputImageType::RegionType OutputImageRegionType;
   typedef typename     OutputImageType::PixelType  OutputImagePixelType;
 
+  typedef TAccumulator AccumulatorType;
 
   /** ImageDimension enumeration */
   itkStaticConstMacro(InputImageDimension, unsigned int,
@@ -106,7 +107,7 @@ protected:
    *     ImageToImageFilter::GenerateData()  */
   void GenerateData(void);
 
-  virtual TAccumulator NewAccumulator( unsigned long );
+  virtual AccumulatorType NewAccumulator( unsigned long );
 
 private:
   ProjectionImageFilter(const Self&); //purposely not implemented

### 2006-02-11 itkBinaryProjectionImageFilter.h
add binary projection
darcs-hash:20060211174426-2fc9d-79f71d47abc73a7d7c91e7fe6742461cf5febb21.gz

@@ -1,0 +1,132 @@
+#ifndef __itkBinaryProjectionImageFilter_h
+#define __itkBinaryProjectionImageFilter_h
+
+#include "itkProjectionImageFilter.h"
+#include "itkNumericTraits.h"
+
+namespace itk {
+/** \class BinaryProjectionImageFilter
+ * \brief Binary projection
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \sa ProjectionImageFilter
+ */
+
+
+namespace Function {
+template <class TInputPixel, class TOutputPixel, class TIndexType>
+class BinaryAccumulator
+{
+public:
+  BinaryAccumulator( unsigned long size )
+    {
+    m_IsForeground = false;
+    }
+  ~BinaryAccumulator(){}
+
+  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
+    {
+    if( input == m_ForegroundValue )
+      { m_IsForeground = true; }
+    }
+
+  inline TOutputPixel GetValue()
+    {
+    if( m_IsForeground )
+      { return (TOutputPixel)m_ForegroundValue; }
+    else
+      { return m_BackgroundValue; }
+    }
+
+  bool m_IsForeground;
+
+  TInputPixel m_ForegroundValue;
+
+  TOutputPixel m_BackgroundValue;
+};
+} // end namespace Function
+
+
+template <class TInputImage, class TOutputImage>
+class ITK_EXPORT BinaryProjectionImageFilter :
+    public
+    ProjectionImageFilter<TInputImage, TOutputImage, Function::BinaryAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType, typename TInputImage::IndexType > >
+{
+public:
+  typedef BinaryProjectionImageFilter Self;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::BinaryAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType, typename TInputImage::IndexType > > Superclass;
+
+  typedef SmartPointer<Self>   Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Runtime information support. */
+  itkTypeMacro(BinaryProjectionImageFilter, ProjectionImageFilter);
+
+  /** Method for creation through the object factory. */
+  itkNewMacro(Self);
+
+  /** Convenient typedefs for simplifying declarations. */
+  typedef TInputImage InputImageType;
[…]

### 2006-02-11 itkBinaryProjectionImageFilter.h
call NewAccumulator only one time per update
darcs-hash:20060211183247-2fc9d-a0dd0a17284369ce7023ade3a9c0e3062bbda1bd.gz

@@ -19,11 +19,13 @@ template <class TInputPixel, class TOutputPixel, class TIndexType>
 class BinaryAccumulator
 {
 public:
-  BinaryAccumulator( unsigned long size )
+  BinaryAccumulator( unsigned long size ) {}
+  ~BinaryAccumulator(){}
+
+  inline void Init()
     {
     m_IsForeground = false;
     }
-  ~BinaryAccumulator(){}
 
   inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {

### 2006-02-11 itkMaximumProjectionImageFilter.h

@@ -19,11 +19,13 @@ template <class TInputPixel, class TIndexType>
 class MaximumAccumulator
 {
 public:
-  MaximumAccumulator( unsigned long size )
+  MaximumAccumulator( unsigned long size ) {}
+  ~MaximumAccumulator(){}
+
+  inline void Init()
     {
     m_Maximum = NumericTraits< TInputPixel >::NonpositiveMin();
     }
-  ~MaximumAccumulator(){}
 
   inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {

### 2006-02-11 itkMeanProjectionImageFilter.h

@@ -23,10 +23,14 @@ public:
 
   MeanAccumulator( unsigned long size )
     {
-    m_Sum = NumericTraits< TAccumulate >::Zero;
     m_Size = size;
     }
   ~MeanAccumulator(){}
+
+  inline void Init()
+    {
+    m_Sum = NumericTraits< TAccumulate >::Zero;
+    }
 
   inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {

### 2006-02-11 itkMedianProjectionImageFilter.h

@@ -27,6 +27,11 @@ public:
     }
   ~MedianAccumulator(){}
 
+  inline void Init()
+    {
+    m_Values.clear();
+    }
+
   inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {
     m_Values.push_back( input );

### 2006-02-11 itkMinimumProjectionImageFilter.h

@@ -19,11 +19,13 @@ template <class TInputPixel, class TIndexType>
 class MinimumAccumulator
 {
 public:
-  MinimumAccumulator( unsigned long size )
+  MinimumAccumulator( unsigned long size ) {}
+  ~MinimumAccumulator(){}
+
+  inline void Init()
     {
     m_Minimum = NumericTraits< TInputPixel >::max();
     }
-  ~MinimumAccumulator(){}
 
   inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {

### 2006-02-11 itkSigmaProjectionImageFilter.h

@@ -23,11 +23,16 @@ public:
 
   SigmaAccumulator( unsigned long size )
     {
-    m_Sum = NumericTraits< TAccumulate >::Zero;
     m_Size = size;
     m_Values.reserve( size );
     }
   ~SigmaAccumulator(){}
+
+  inline void Init()
+    {
+    m_Sum = NumericTraits< TAccumulate >::Zero;
+    m_Values.clear();
+    }
 
   inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {

### 2006-02-11 itkSumProjectionImageFilter.h

@@ -19,11 +19,13 @@ template <class TInputPixel, class TOuputPixel, class TIndexType>
 class SumAccumulator
 {
 public:
-  SumAccumulator( unsigned long size )
+  SumAccumulator( unsigned long size ) {}
+  ~SumAccumulator(){}
+
+  inline void Init()
     {
     m_Sum = NumericTraits< TOuputPixel >::Zero;
     }
-  ~SumAccumulator(){}
 
   inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
     {

### 2006-02-11 itkProjectionImageFilter.h
the filter is now threaded
darcs-hash:20060211211643-2fc9d-82d4c0f961b40177ec01c836721bfe6f79d88152.gz

@@ -101,13 +101,11 @@ protected:
   /** Apply changes to the input image requested region. */
   virtual void GenerateInputRequestedRegion();
 
-  /** This method implements the actual accumulation of the image.
-   *
-   * \sa ImageToImageFilter::ThreadedGenerateData(),
-   *     ImageToImageFilter::GenerateData()  */
-  void GenerateData(void);
+  virtual void ThreadedGenerateData( const OutputImageRegionType& outputRegionForThread, int threadId );
 
   virtual AccumulatorType NewAccumulator( unsigned long );
+
+  virtual int SplitRequestedRegion( int i, int num, OutputImageRegionType& splitRegion );
 
 private:
   ProjectionImageFilter(const Self&); //purposely not implemented

### 2006-02-12 itkSigmaProjectionImageFilter.h
avoid division by zero
darcs-hash:20060212175003-2fc9d-5d55421920bd482fabc2210ff5ad4016f42a58d2.gz

@@ -42,6 +42,10 @@ public:
 
   inline RealType GetValue()
     {
+    // to avoid division by zero
+    if( m_Size <= 1 )
+      return NumericTraits<RealType>::Zero;
+
     typename NumericTraits<TInputPixel>::RealType mean = ((RealType) m_Sum) / m_Size;
     typename std::vector<TInputPixel>::iterator it;
     RealType squaredSum = NumericTraits<RealType>::Zero;

### 2006-02-12 itkProjectionImageFilter.h
use ProjectionDimesion instead of Axe, as suggested by Jim Miller
darcs-hash:20060212180323-2fc9d-c9a0bc08dded29aedd331290148f3ccbaa5699af.gz

@@ -28,7 +28,7 @@ namespace itk
  *
  *    This class accumulates an image along a dimension and reduce the size 
  * of this dimension to 1. The dimension being accumulated is set by 
- * Axe. 
+ * ProjectionDimension. 
  *
  *   Each pixel is the cumulative sum of the pixels along the collapsed
  * dimension and reduce the size of the accumulated dimension to 1 (only 
@@ -86,8 +86,8 @@ public:
   /** Set the direction in which to accumulate the data.  It must be
    * set before the update of the filter. Defaults to the last
    * dimension. */
-  itkGetMacro( Axe, unsigned int );
-  itkSetMacro( Axe, unsigned int );
+  itkGetMacro( ProjectionDimension, unsigned int );
+  itkSetMacro( ProjectionDimension, unsigned int );
 
 
 protected:
@@ -111,7 +111,7 @@ private:
   ProjectionImageFilter(const Self&); //purposely not implemented
   void operator=(const Self&); //purposely not implemented
 
-  unsigned int m_Axe;
+  unsigned int m_ProjectionDimension;
 
 };
 

### 2006-02-12 itkProjectionImageFilter.h
drop the SplitRequestedRegion() method - it is not needed
darcs-hash:20060212180840-2fc9d-7994c6b28df03195a155fdb1ef9aec6f89ee228b.gz

@@ -105,8 +105,6 @@ protected:
 
   virtual AccumulatorType NewAccumulator( unsigned long );
 
-  virtual int SplitRequestedRegion( int i, int num, OutputImageRegionType& splitRegion );
-
 private:
   ProjectionImageFilter(const Self&); //purposely not implemented
   void operator=(const Self&); //purposely not implemented

### 2006-02-12 itkBinaryProjectionImageFilter.h
drop the index part
darcs-hash:20060212181742-2fc9d-c0de2f4354def922211cff20baa278957ebb4c75.gz

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TOutputPixel, class TIndexType>
+template <class TInputPixel, class TOutputPixel>
 class BinaryAccumulator
 {
 public:
@@ -27,7 +27,7 @@ public:
     m_IsForeground = false;
     }
 
-  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
+  inline TInputPixel operator()( const TInputPixel &input )
     {
     if( input == m_ForegroundValue )
       { m_IsForeground = true; }
@@ -53,11 +53,11 @@ public:
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT BinaryProjectionImageFilter :
     public
-    ProjectionImageFilter<TInputImage, TOutputImage, Function::BinaryAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType, typename TInputImage::IndexType > >
+    ProjectionImageFilter<TInputImage, TOutputImage, Function::BinaryAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType > >
 {
 public:
   typedef BinaryProjectionImageFilter Self;
-  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::BinaryAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType, typename TInputImage::IndexType > > Superclass;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::BinaryAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-12 itkMaximumProjectionImageFilter.h

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TIndexType>
+template <class TInputPixel>
 class MaximumAccumulator
 {
 public:
@@ -27,7 +27,7 @@ public:
     m_Maximum = NumericTraits< TInputPixel >::NonpositiveMin();
     }
 
-  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
+  inline TInputPixel operator()( const TInputPixel &input )
     {
     m_Maximum = vnl_math_max( m_Maximum, input );
     }
@@ -45,11 +45,11 @@ public:
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT MaximumProjectionImageFilter :
     public
-    ProjectionImageFilter<TInputImage, TOutputImage, Function::MaximumAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > >
+    ProjectionImageFilter<TInputImage, TOutputImage, Function::MaximumAccumulator< typename TInputImage::PixelType > >
 {
 public:
   typedef MaximumProjectionImageFilter Self;
-  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MaximumAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > > Superclass;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MaximumAccumulator< typename TInputImage::PixelType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-12 itkMeanProjectionImageFilter.h

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TAccumulate, class TIndexType>
+template <class TInputPixel, class TAccumulate>
 class MeanAccumulator
 {
 public:
@@ -32,7 +32,7 @@ public:
     m_Sum = NumericTraits< TAccumulate >::Zero;
     }
 
-  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
+  inline TInputPixel operator()( const TInputPixel &input )
     {
     m_Sum = m_Sum + input;
     }
@@ -52,12 +52,12 @@ template <class TInputImage, class TOutputImage, class TAccumulate=typename Nume
 class ITK_EXPORT MeanProjectionImageFilter :
     public
     ProjectionImageFilter<TInputImage, TOutputImage,
-      Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate, typename TInputImage::IndexType > >
+      Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate > >
 {
 public:
   typedef MeanProjectionImageFilter Self;
   typedef ProjectionImageFilter<TInputImage, TOutputImage, 
-    Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate, typename TInputImage::IndexType > > Superclass;
+    Function::MeanAccumulator< typename TInputImage::PixelType, TAccumulate > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-12 itkMedianProjectionImageFilter.h

@@ -17,7 +17,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TIndexType>
+template <class TInputPixel>
 class MedianAccumulator
 {
 public:
@@ -32,7 +32,7 @@ public:
     m_Values.clear();
     }
 
-  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
+  inline TInputPixel operator()( const TInputPixel &input )
     {
     m_Values.push_back( input );
     }
@@ -52,11 +52,11 @@ public:
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT MedianProjectionImageFilter :
     public
-    ProjectionImageFilter<TInputImage, TOutputImage, Function::MedianAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > >
+    ProjectionImageFilter<TInputImage, TOutputImage, Function::MedianAccumulator< typename TInputImage::PixelType > >
 {
 public:
   typedef MedianProjectionImageFilter Self;
-  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MedianAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > > Superclass;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MedianAccumulator< typename TInputImage::PixelType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-12 itkMinimumProjectionImageFilter.h

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TIndexType>
+template <class TInputPixel>
 class MinimumAccumulator
 {
 public:
@@ -27,7 +27,7 @@ public:
     m_Minimum = NumericTraits< TInputPixel >::max();
     }
 
-  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
+  inline TInputPixel operator()( const TInputPixel &input )
     {
     m_Minimum = vnl_math_min( m_Minimum, input );
     }
@@ -45,11 +45,11 @@ public:
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT MinimumProjectionImageFilter :
     public
-    ProjectionImageFilter<TInputImage, TOutputImage, Function::MinimumAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > >
+    ProjectionImageFilter<TInputImage, TOutputImage, Function::MinimumAccumulator< typename TInputImage::PixelType > >
 {
 public:
   typedef MinimumProjectionImageFilter Self;
-  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MinimumAccumulator< typename TInputImage::PixelType, typename TInputImage::IndexType > > Superclass;
+  typedef ProjectionImageFilter<TInputImage, TOutputImage, Function::MinimumAccumulator< typename TInputImage::PixelType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-12 itkSigmaProjectionImageFilter.h

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TAccumulate, class TIndexType>
+template <class TInputPixel, class TAccumulate>
 class SigmaAccumulator
 {
 public:
@@ -34,7 +34,7 @@ public:
     m_Values.clear();
     }
 
-  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
+  inline TInputPixel operator()( const TInputPixel &input )
     {
     m_Sum = m_Sum + input;
     m_Values.push_back( input );
@@ -67,12 +67,12 @@ template <class TInputImage, class TOutputImage, class TAccumulate=typename Nume
 class ITK_EXPORT SigmaProjectionImageFilter :
     public
     ProjectionImageFilter<TInputImage, TOutputImage,
-      Function::SigmaAccumulator< typename TInputImage::PixelType, TAccumulate, typename TInputImage::IndexType > >
+      Function::SigmaAccumulator< typename TInputImage::PixelType, TAccumulate > >
 {
 public:
   typedef SigmaProjectionImageFilter Self;
   typedef ProjectionImageFilter<TInputImage, TOutputImage, 
-    Function::SigmaAccumulator< typename TInputImage::PixelType, TAccumulate, typename TInputImage::IndexType > > Superclass;
+    Function::SigmaAccumulator< typename TInputImage::PixelType, TAccumulate > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-12 itkSumProjectionImageFilter.h

@@ -15,7 +15,7 @@ namespace itk {
 
 
 namespace Function {
-template <class TInputPixel, class TOuputPixel, class TIndexType>
+template <class TInputPixel, class TOuputPixel>
 class SumAccumulator
 {
 public:
@@ -27,7 +27,7 @@ public:
     m_Sum = NumericTraits< TOuputPixel >::Zero;
     }
 
-  inline TInputPixel operator()( const TInputPixel &input, const TIndexType &index )
+  inline TInputPixel operator()( const TInputPixel &input )
     {
     m_Sum = m_Sum + input;
     }
@@ -46,12 +46,12 @@ template <class TInputImage, class TOutputImage>
 class ITK_EXPORT SumProjectionImageFilter :
     public
     ProjectionImageFilter<TInputImage, TOutputImage,
-      Function::SumAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType, typename TInputImage::IndexType > >
+      Function::SumAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType > >
 {
 public:
   typedef SumProjectionImageFilter Self;
   typedef ProjectionImageFilter<TInputImage, TOutputImage, 
-    Function::SumAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType, typename TInputImage::IndexType > > Superclass;
+    Function::SumAccumulator< typename TInputImage::PixelType, typename TOutputImage::PixelType > > Superclass;
 
   typedef SmartPointer<Self>   Pointer;
   typedef SmartPointer<const Self>  ConstPointer;

### 2006-02-12 article/Article.tex
add sigma projection
darcs-hash:20060211120717-2fc9d-d551ef7f2866c3802acb6209b295cb2667e56cc4.gz
enhance the article
darcs-hash:20060212220651-2fc9d-eb0a1bf23226000511562e56af95bd9d85b27bf6.gz

@@
 % the relevant document. 
-\title{Image projections along an axe}
+\title{Image projections along an axis}
 
@@
 \doxygen{AccumulateImageFilter}. However, this class is limited to sum
-projection and mean projection.
+and mean projections.
 
@@
 
-The base class, ProjectionImageFilter, is mainly a copy of
-AccumulateImageFilter, with some enhancement:
+The base class, \verb$ProjectionImageFilter$, is mainly a copy of
+\verb$AccumulateImageFilter$, with some enhancement:
 \begin{itemize}
@@
   \item report its progress
+  \item thread support
 \end{itemize}
@@
 \begin{itemize}
-  \item maximum projection (MaximumProjectionImageFilter)
-  \item minimum projection (MinimumProjectionImageFilter)
-  \item mean projection (MeanProjectionImageFilter)
-  \item median projection (MedianProjectionImageFilter)
-  \item sum projection (SumProjectionImageFilter)
+  \item maximum projection (\verb$MaximumProjectionImageFilter$)
+  \item minimum projection (\verb$MinimumProjectionImageFilter$)
+  \item mean projection (\verb$MeanProjectionImageFilter$)
+  \item median projection (\verb$MedianProjectionImageFilter$)
+  \item sum projection (\verb$SumProjectionImageFilter$)
+  \item sigma projection (\verb$SigmaProjectionImageFilter$)
+  \item binary projection (\verb$BinaryProjectionImageFilter$)
 \end{itemize}
 Other projections types can easily be created just by providing a new functor.
+
+The projection can be easily threaded by splitting the required region. The
+Only important thing is to take care to not split the region on the projection
+dimension. 
+The default split done by \verb$ImageSource$ if fully usable without any changes
+because it is done on the output region, and that region have a size of 1 on
+the projection dimension, so the split will be done on anothe dimesion.
 
@@
 As an example, here is a filter which implement a square sum projection along a
-axe. This example may be useful in case of signed input type.
+axis. This example may be useful in case of signed input type.
 
@@
 Now, create the class which do the real work: receive all the pixel values and
-give the result at the end. The class is created in the itk::Function names pace
-to avoid putting to much things in itk name space, and is templated over the
+give the result at the end. The class is created in the \verb$itk::Function$ names pace
+to avoid putting too much things in itk name space, and is templated over the
 type of the input and the output pixel.
-On object of this class is created for each pixel in the output image.
+One object of this class is created for each thread.
 \small \begin{verbatim}
@@
 during the projection. In that case, this parameter is not useful, so it is not
-saved in an attribute of the class. The sum is initialized to zero.
+saved in an attribute of the class.
+
+If some custom parameters need to be passed to the accumulator, the \verb$NewAccumulator()$
+method can be overloaded. See \verb$BinaryProjectionImageFilter$'s code for an
+example.
 
@@
 \small \begin{verbatim}
-  SquareSumAccumulator( unsigned long nb )
+  SquareSumAccumulator( unsigned long size ) {}
+  ~SquareSumAccumulator(){}
+\end{verbatim} \normalsize
+\verb$Init()$ is called before accumulating a new set of pixel
+to initialize the accumulator. Here, the sum is initialized to zero.
+\small \begin{verbatim}
+  void Init()
     {
@@
     }
-  ~SquareSumAccumulator(){}
 \end{verbatim} \normalsize
-The operator() is called for each pixel. In this method, the square sum is
+The \verb$operator()$ is called for all pixels. In this method, the square sum is
 contructed, pixel after pixel. The method is declared inline for best
@@
 \small \begin{verbatim}
-  inline TInputPixel operator()( const TInputPixel &input )
+  inline TOuputPixel operator()( const TInputPixel &input )
     {
-    m_SquareSum = m_SquareSum + ( input * input );
+    m_SquareSum = m_SquareSum + vnl_math_sqr( (TOuputPixel) input );
     }
 \end{verbatim} \normalsize
-GetValue() is called to set the value of the result image. In that example, the
-sum is just return, but more complex computation can be done here (see the
-MedianProjectionImageFilter for an example). ProjectionImageFilter cast the
+\verb$GetValue()$ is called to set the value of the result image. In that example, the
+sum is just returned, but more complex computations can be done here (see the
+\verb$MedianProjectionImageFilter$'s code for an example). \verb$ProjectionImageFilter$ cast the
 output of this method to the output image's pixel type.
@@
 Figure~\ref{maximum0}, Figure~\ref{maximum1}, Figure~\ref{maximum},
-Figure~\ref{minimum}, Figure~\ref{mean} and Figure~\ref{median} show the result
+Figure~\ref{minimum}, Figure~\ref{mean}, Figure~\ref{median},
+Figure~\ref{sigma} and Figure~\ref{binary100} show the result
 of different projection on different axes. The result of
@@
 \includegraphics[scale=0.5]{maximum0}
-\caption{MaximumProjectionImageFilter, projection along axe x.\label{maximum0}}
+\caption{MaximumProjectionImageFilter, projection along axis x.\label{maximum0}}
 \end{figure}
@@
 \includegraphics[scale=0.5]{maximum1}
-\caption{MaximumProjectionImageFilter, projection along axe y.\label{maximum1}}
+\caption{MaximumProjectionImageFilter, projection along axis y.\label{maximum1}}
 \end{figure}
@@
 \includegraphics[scale=0.75]{maximum}
-\caption{MaximumProjectionImageFilter, projection along axe z.\label{maximum}}
+\caption{MaximumProjectionImageFilter, projection along axis z.\label{maximum}}
 \end{figure}
@@
 \includegraphics[scale=0.75]{minimum}
-\caption{MinimumProjectionImageFilter, projection along axe z.\label{minimum}}
+\caption{MinimumProjectionImageFilter, projection along axis z.\label{minimum}}
 \end{figure}
@@
 \includegraphics[scale=0.75]{mean}
-\caption{MeanProjectionImageFilter, projection along axe z.\label{mean}}
+\caption{MeanProjectionImageFilter, projection along axis z.\label{mean}}
 \end{figure}
@@
 \includegraphics[scale=0.75]{median}
-\caption{MedianProjectionImageFilter, projection along axe z\label{median}}
+\caption{MedianProjectionImageFilter, projection along axis z\label{median}}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=0.75]{sigma}
+\caption{SigmaProjectionImageFilter, projection along axis z\label{sigma}}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=0.75]{binary100}
+\caption{BinaryProjectionImageFilter, projection along axis z, with foreground value = 100, and background value = 255\label{binary100}}
 \end{figure}
@@
 \small \begin{verbatim}
-#include "itkImageFileReader.h"
-#include "itkImageFileWriter.h"
-#include "itkCommand.h"
 #include "itkSimpleFilterWatcher.h"
@@
 {
-  int axe = atoi(argv[1]);
+  int dim = atoi(argv[1]);
 
@@
   filter->SetInput( reader->GetOutput() );
-  filter->SetAxe( axe );
+  filter->SetProjectionDimension( dim );
+  // to be sure that the result is ok with several threads, even on a single
+  // proc computer
+  filter->SetNumberOfThreads( 2 );
 
@@
   for(int i=0; i<=3; i++) {
-    if(i == axe) {
+    if(i == dim) {
       size[i] = 0;
@@
   extract->SetExtractionRegion( region );
+
+  std::cout << "size: " << size << std::endl;
+  std::cout << "index: " << idx << std::endl;
+
+  extract->Update();
+  std::cout << "output size: " << extract->GetOutput()->GetLargestPossibleRegion().GetSize() << std::endl;
 

### 2006-02-19 article/Article.tex
complete the article and add timing results
darcs-hash:20060219095448-2fc9d-e9b158b89cf455198e0e4075645c3737a1a405be.gz

@@
 \section{Introduction}
-ITK already provide a class to project an image along an axe:
+ITK already provide a class to project an image along an axis:
 \doxygen{AccumulateImageFilter}. However, this class is limited to sum
@@
 The projection can be easily threaded by splitting the required region. The
-Only important thing is to take care to not split the region on the projection
+only important thing is to take care to not split the region on the projected
 dimension.
@@
 because it is done on the output region, and that region have a size of 1 on
-the projection dimension, so the split will be done on anothe dimesion.
+the projected dimension, so the split will be done on another dimension.
 
-AccumulateImageFilter is not modifiable to implement functor support without
-breaking the API.
+\verb$AccumulateImageFilter$ is not modifiable to implement functor support without
+breaking the API. However, \verb$AccumulateImageFilter$ can be implemented as a
+sub-class of \verb$ProjectionImageFilter$ to benefit of the thread support, and to
+avoid duplication of code.
 
-\section{Implemeting a new projection method}
+\section{Implementing a new projection method}
 As an example, here is a filter which implement a square sum projection along a
@@
 
-Everything can be done in a single file, itkSquareSumProjectionImageFilter.h.
+Everything can be done in a single file, \verb$itkSquareSumProjectionImageFilter.h$.
 \small \begin{verbatim}
@@
 \end{verbatim} \normalsize
-The itkProjectionImageFilter.h header must be included.
+The \verb$itkProjectionImageFilter.h$ header must be included.
 \small \begin{verbatim}
@@
 Now, create the class which do the real work: receive all the pixel values and
-give the result at the end. The class is created in the \verb$itk::Function$ names pace
-to avoid putting too much things in itk name space, and is templated over the
+give the result at the end. The class is created in the \verb$itk::Function$ name space
+to avoid putting too much things in the \verb$itk$ name space, and is templated over the
 type of the input and the output pixel.
@@
 \end{verbatim} \normalsize
-\verb$Init()$ is called before accumulating a new set of pixel
+\verb$Init()$ is called before accumulating a new set of pixels
 to initialize the accumulator. Here, the sum is initialized to zero.
@@
 The \verb$operator()$ is called for all pixels. In this method, the square sum is
-contructed, pixel after pixel. The method is declared inline for best
+constructed, pixel after pixel. The method is declared \verb$inline$ for best
 performance.
@@
 \end{verbatim} \normalsize
-\verb$GetValue()$ is called to set the value of the result image. In that example, the
+\verb$GetValue()$ is called to set the value of the pixel in the output image. In that example, the
 sum is just returned, but more complex computations can be done here (see the
@@
 \end{verbatim} \normalsize
-The class is declared. It inherits from ProjectionImageFilter, and declares the
+The class is declared. It inherits from \verb$ProjectionImageFilter$, and declares the
 usual types and methods.
@@
 A timing test comparing performance on a $371 \times 371 \times 34$
-image showed that the results are similar with AccumulateImageFilter
-and the equivalent ProjectionImageFilter, and that the new projection
-types have similar performance. The results achieved on an Athlon 64 
-Processor 2800+ (1802 MHz) with 512Kb cache, 512 Mb of RAM and gcc
-4.0.2 are shown in Table~\ref{perf}.
+image showed that the new filter outperform the current implementation,
+while it should have very similar performance.
+This is the result of a problem in ITK 2.4.1, where the iterator with index
+is a lot more efficient than the one without index. The new implementation
+use the iterator with index for best performance, but really don't need
+it, and should get even better performance with the iterator without
+index once this problem will be fixed.
+
+ The results achieved on an server with 4 Intel(R) Xeon(TM) MP CPU 3.66GHz
+with 1024Kb cache, 24 Gb of RAM, hyperthreading activated, gcc
+3.4.3 and running Mandriva Linux are shown in Table~\ref{perf} and
+Figure~\ref{results}.
 
@@
 \hline
-MaximumProjectionImageFilter & 0.652 s \\
-MinimumProjectionImageFilter  & 0.614 s\\
-SumProjectionImageFilter  & 0.614 s\\
-MeanProjectionImageFilter  & 0.619 s\\
-MedianProjectionImageFilter  & 0.831 s\\
-AccumulateImageFilter, sum  & 0.615 s\\
-AccumulateImageFilter, mean  & 0.617 s\\
+\verb$MaximumProjectionImageFilter$ & 0.0841 s \\
+\verb$MinimumProjectionImageFilter$  & 0.0846 s\\
+\verb$SumProjectionImageFilter$  & 0.0872 s\\
+\verb$MeanProjectionImageFilter$  & 0.0828 s\\
+\verb$MedianProjectionImageFilter$  & 0.164 s\\
+\verb$SigmaProjectionImageFilter$  & 0.123 s\\
+\verb$BinaryProjectionImageFilter$  & 0.0848 s\\
+\verb$AccumulateImageFilter$, sum  & 0.465 s\\
+\verb$AccumulateImageFilter$, mean  & 0.465 s\\
 \hline
 \end{tabular}
-\caption{Execution time.\label{perf}}
+\caption{Execution time with a single thread.\label{perf}}
 \end{table}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{results}
+\caption{Execution time with an increasing number of threads.\label{results}}
+\end{figure}
+
+Figure~\ref{results} show a important increase of performance while using several
+threads\footnote{It also show that the execution time is not really stable
+and that the mean of 50 execution time is not enough to compare the execution
+time with precision. This will be discussed in another article.}.
+
+Note that above 4 threads, the execution times are still decreasing. In that case,
+hyperthreading give an increase of performance.
 
@@
 of different projection on different axes. The result of
-SumProjectionImageFilter in similar to the result of MeanProjectionImageFilter,
+\verb$SumProjectionImageFilter$ in similar to the result of \verb$MeanProjectionImageFilter$,
 but with a higher range of values, and so is not shown here.
@@
 performance than the current available filter, but loss the compatibility with
-the previous filter. I propose to mark AccumulateImageFilter as deprecated in
+the previous filter. I propose to mark \verb$AccumulateImageFilter$ as deprecated in
 the next release of ITK to incite ITK user to use the new class.

### 2006-03-02 itkProjectionImageFilter.h
add N-1 dimension support (still broken)
darcs-hash:20060302185807-2fc9d-1896dda1082b8234dd7c330bcdad4880354ddaf7.gz

@@ -79,9 +79,9 @@ public:
                       TOutputImage::ImageDimension);
 
   /** Input and output images must be the same dimension. */
-  itkConceptMacro(ImageDimensionCheck,
-      (Concept::SameDimension<itkGetStaticConstMacro(InputImageDimension),
-                              itkGetStaticConstMacro(OutputImageDimension)>));
+//   itkConceptMacro(ImageDimensionCheck,
+//       (Concept::SameDimension<itkGetStaticConstMacro(InputImageDimension),
+//                               itkGetStaticConstMacro(OutputImageDimension)>));
 
   /** Set the direction in which to accumulate the data.  It must be
    * set before the update of the filter. Defaults to the last

### 2006-03-02 article/Article.tex
small fixes
darcs-hash:20060302202053-2fc9d-eda897a441ddf9e03b8b30cf5607aba46fd7cb33.gz

@@
 \hline
-Filter & execution time \\
+Filter & Execution time \\
 \hline
@@
 
-Figure~\ref{results} show a important increase of performance while using several
+Figure~\ref{results} show an important increase of performance while using several
 threads\footnote{It also show that the execution time is not really stable
@@
 \centering
-\includegraphics[scale=0.5]{maximum0}
+\includegraphics[scale=0.75]{maximum2D0}
 \caption{MaximumProjectionImageFilter, projection along axis x.\label{maximum0}}
@@
 \centering
-\includegraphics[scale=0.5]{maximum1}
+\includegraphics[scale=0.75]{maximum2D1}
 \caption{MaximumProjectionImageFilter, projection along axis y.\label{maximum1}}

### 2006-03-03 article/Article.tex
continue article
darcs-hash:20060303132903-2fc9d-f8541dc931fe1ae82df0cddc2898fbd8be6394e5.gz

@@
 \section{Introduction}
-ITK already provide a class to project an image along an axis:
-\doxygen{AccumulateImageFilter}. However, this class is limited to sum
-and mean projections.
+Image projection is a very common task in image analysis to reduce the dimension
+of an image. ITK already provide a class to project an image along an axis:
+\doxygen{AccumulateImageFilter}. However, this class is not very efficient,
+hard to extend, and not able to produce an image with a smaller dimension than
+the input image.
+
+Like \verb$AccumulateImageFilter$, \verb$ProjectionImageFilter$ can produce an
+ouput image with the same dimension than the input image. In that case, all
+the informations associated to the input image are copied to the output one,
+and excepted:
+\begin{itemize}
+  \item the size of the image which is set to 1 on the projection dimension,
+  \item the spacing of the image, which is modified on the projection dimension
+to keep the physical size of the image on the output image,
+  \item the index of the image wich is set to 0 on the projection dimension.
+\end{itemize}
+Basically, \verb$ProjectionImageFilter$ produce the same volume but with a
+only 1 pixel on the projection dimension.
+
+Unlike the \verb$AccumulateImageFilter$, \verb$ProjectionImageFilter$ can 
+also produce an ouput image with a dimension lower than the input image.
+While it is logical to produce a 2D image with a projection of a 3D image,
+it also bring some more complex transforms, because the dimensions of the
+input image can't be directly copied to the input image - one dimension is
+removed. \verb$ProjectionImageFilter$ move the removed dimension of the
+input image to the projected dimension in the output image. With a 3D
+input image, the output will be:
+\begin{itemize}
+  \item projection along the axe x:
+	\begin{itemize}
+	\item x is removed
+	\item y stay y in the output image
+	\item z become x in the output image
+	\end{itemize}
+  \item projection along the axe y:
+	\begin{itemize}
+	\item x stay x in the output image
+	\item y is removed
+	\item z become y in the output image
+	\end{itemize}
+  \item projection along the axe z:
+	\begin{itemize}
+	\item x stay x in the output image
+	\item y stay y in the output image
+	\item z is removed.
+	\end{itemize}
+       No dimension is moved in that case.
+\end{itemize}
+
+Also, during the projection, there is an orientation problem which doesn't
+exist if the number of dimensions is kept.
+
+\small \begin{verbatim}
+        ________
+       /       /|            /|
+      /       / |           / |
+ 1   /_______/  |  2       /  |
+ --> |       |  |<--       |  |
+     |       | 0/          | 0/
+     |       | /           | /
+     |_______|/            |/
+\end{verbatim} \normalsize
+
+On the volume above, the image is projected on the horizontal dimension.
+If the number of dimension is not modified, a thin volume with a size of
+1 on projection dimension, and there is no problem.
+
+If the number of dimensions is reduced, the direction become important,
+and the result is not the same.
+
+\small \begin{verbatim}
+      _______
+     |0      |
+ 1   |       |
+     |_______|
+      _______
+     |      0|
+ 2   |       |
+     |_______|
+\end{verbatim} \normalsize
+
+However, we choose to move the dimensions and the indexes on those
+dimensions, and so to not provide the ability to choose the direction.
+The image is always projected with direction 1.
+The user can still modify the output image with ITK filters like
+\doxygen{FlipImageFilter}.
 
@@
 
-The base class, \verb$ProjectionImageFilter$, is mainly a copy of
+The base class, \verb$ProjectionImageFilter$, is a re-write of
 \verb$AccumulateImageFilter$, with some enhancement:
@@
 \includegraphics[scale=0.75]{maximum2D0}
-\caption{MaximumProjectionImageFilter, projection along axis x.\label{maximum0}}
+\caption{MaximumProjectionImageFilter, projection along axis x. Note that the orientation
+is the correct one: the axis z (34 pixels) have been moved to the axis x, and the axis y
+(371 pixels) is not modified. Also, the image shown here does not respect the spacing
+of the image, but ProjectionImageFilter does.\label{maximum0}}
 \end{figure}

### 2006-03-05 article/Article.tex
update timing and article
darcs-hash:20060305182553-2fc9d-a8da8ec3ed19cedb00b64321325af02ef22e40d4.gz

@@
 of an image. A base filter is provided with some specialized filters which
-implement different projection methods.
+implement efficiently different projection methods.
 \end{abstract}
@@
 \end{itemize}
-Basically, \verb$ProjectionImageFilter$ produce the same volume but with a
+Basically, \verb$ProjectionImageFilter$ produce the same volume but with
 only 1 pixel on the projection dimension.
@@
 
-However, we choose to move the dimensions and the indexes on those
-dimensions, and so to not provide the ability to choose the direction.
+However, we choose to move the dimensions {\em and} the indexes on those
+dimensions, and so, to not provide the ability to choose the direction.
 The image is always projected with direction 1.
@@
 \begin{itemize}
-  \item projection is delegated to a functor
-  \item report its progress
-  \item thread support
+  \item projection is delegated to a functor,
+  \item report its progress,
+  \item thread support,
+  \item dimension of ouput image can be smaller than dimension of the input image.
 \end{itemize}
@@
 A timing test comparing performance on a $371 \times 371 \times 34$
-image showed that the new filter outperform the current implementation,
-while it should have very similar performance.
-This is the result of a problem in ITK 2.4.1, where the iterator with index
-is a lot more efficient than the one without index. The new implementation
-use the iterator with index for best performance, but really don't need
-it, and should get even better performance with the iterator without
-index once this problem will be fixed.
+image showed that the new filter have better performance than the
+\verb$AccumulateImageFilter$ for axis y and z, but worth for the x
+axis. This is the result of the usage of a linear iterator in
+\verb$ProjectionImageFilter$ and an image region iterator in
+\verb$AccumulateImageFilter$.
 
@@
 
+% #dim    size    max     min     sum     accSum  mean    accMean median  sigma   binary
+% 0       371     0.02    0.02    0.0116  0.0128  0.0105  0.0128  0.0619  0.0504  0.019
+% 1       371     0.0218  0.0218  0.0157  0.425   0.0153  0.424   0.0705  0.0538  0.021
+% 2       34      0.0308  0.0308  0.0222  0.459   0.0223  0.46    0.104   0.0683  0.0299
 \begin{table}[htbp]
 \centering
-\begin{tabular}{cc}
+\begin{tabular}{cccc}
 \hline
-Filter & Execution time \\
+Filter & Axis: x & Axis: y & Axis: z \\
 \hline
 \hline
-\verb$MaximumProjectionImageFilter$ & 0.0841 s \\
-\verb$MinimumProjectionImageFilter$  & 0.0846 s\\
-\verb$SumProjectionImageFilter$  & 0.0872 s\\
-\verb$MeanProjectionImageFilter$  & 0.0828 s\\
-\verb$MedianProjectionImageFilter$  & 0.164 s\\
-\verb$SigmaProjectionImageFilter$  & 0.123 s\\
-\verb$BinaryProjectionImageFilter$  & 0.0848 s\\
-\verb$AccumulateImageFilter$, sum  & 0.465 s\\
-\verb$AccumulateImageFilter$, mean  & 0.465 s\\
+\verb$MaximumProjectionImageFilter$  & 0.02 s   & 0.0218 s & 0.0308 s \\
+\verb$MinimumProjectionImageFilter$  & 0.02 s   & 0.0218 s & 0.0308 s\\
+\verb$MedianProjectionImageFilter$   & 0.0619 s & 0.0705 s & 0.104 s \\
+\verb$SigmaProjectionImageFilter$    & 0.0504 s & 0.0538 s & 0.0683 s\\
+\verb$BinaryProjectionImageFilter$   & 0.019  s & 0.021 s  & 0.0299 s\\
+\verb$SumProjectionImageFilter$      & 0.0116 s & 0.0157 s & 0.0222 s\\
+\verb$MeanProjectionImageFilter$     & 0.0105 s & 0.0153 s & 0.0223 s\\
+\hline
+\verb$AccumulateImageFilter$, sum    & 0.0128 s & 0.425 s  & 0.459 s \\
+\verb$AccumulateImageFilter$, mean   & 0.0128 s & 0.424 s  & 0.46 s  \\
 \hline
@@
 \includegraphics{results}
-\caption{Execution time with an increasing number of threads.\label{results}}
+\caption{Execution time with an increasing number of threads. Projection axis is z.\label{results}}
 \end{figure}
 
-Figure~\ref{results} show an important increase of performance while using several
-threads\footnote{It also show that the execution time is not really stable
-and that the mean of 50 execution time is not enough to compare the execution
-time with precision. This will be discussed in another article.}.
+% #th     max
+% 1       0.0311
+% 2       0.0197
+% 3       0.017
+% 4       0.0161
+% 5       0.015
+% 6       0.013
+% 7       0.0119
+% 8       0.0108
+% 9       0.0116
+% 10      0.0115
+\begin{table}[htbp]
+\centering
+\begin{tabular}{ccc}
+\hline
+Number of threads & Execution time & Speedup \\
+\hline
+\hline
+1      & 0.0311 s & 1 \\
+2      & 0.0197 s & 1.58\\
+3      & 0.017  s & 1.83\\
+4      & 0.0161 s & 1.93\\
+5      & 0.015  s & 2.07\\
+6      & 0.013  s & 2.39\\
+7      & 0.0119 s & 2.61\\
+8      & 0.0108 s & 2.88\\
+9      & 0.0116 s & 2.68\\
+10     & 0.0115 s & 2.7\\
+\hline
+\end{tabular}
+\caption{Execution time and speedup with an increasing number of threads.\label{thread}}
+\end{table}
+
+Figure~\ref{results} and Table~\ref{thread} show an important increase of performance while using several
+threads.
 
